Correcting for bias in high throughput sequencing data

### 2011-06-17 seqbias-paper.tex
all new data, plots

\begin{figure*}
\centerline{\includegraphics[width=\textwidth]{fig/models.eps}}
%% TODO: caption
\caption{Blah blah blah.}
\label{fig:models}
\end{figure*}

@@

\begin{table}
\processtable{
    The $R^2$ goodness of fit statistic measures increased uniformity in read
    coverage, after correcting for bias. Here the median $R^2$ across the test
    exons is listed for each method and simple. A positive $R^2$ indicates a
    better fit.\label{tab:pois}}{
    \begin{tabular}{lcccc}\toprule
          & BN    & MART  & GLM   & 7mer \\\midrule
Wetterbom & 0.173 & 0.016 & 0.066 & -0.079 \\
Katze     & 0.286 & 0.243 & 0.158 & 0.033 \\
Bullard   & 0.276 & 0.163 & 0.224 & 0.157 \\
Mortazavi & 0.248 & 0.210 & 0.197 & 0.091 \\
Trapnell  & 0.308 & 0.289 & 0.248 & 0.138
    \end{tabular}
}{}
\end{table}

@@

RNA-Seq is most often used to compare levels of expression, and so a natural
concern is the consistency of the bias between samples. In the data we examined,
the bias appears to be largely, but not entirely consistent (see,
Supplementary Section 5).
%% TODO: which actual section ?
Similarly, in Figure \ref{fig:freqs}, the three data sets
sequenced on the Illumina platform display similar patterns of nonuniformity,
yet differ in magnitude. Batch effects in RNA-Seq remain a legitimate concern,
that should be evaluated and corrected for.

>>>>

\begin{figure*}
\centerline{\includegraphics[width=\textwidth]{fig/models.eps}}
\caption{
The network structures learned on each of the data sets are examined. Positions
are relative to the read start, which is labeled 0. Hollow circles indicate
position that were not included in the model, being deemed uninformative, give
the other positions and edges. The number of parameters of parameters needed to
specify each model is listed in parenthesis below.}
\label{fig:models}
\end{figure*}

@@

\begin{table}
\processtable{
    The $R^2$ goodness of fit statistic measures increased uniformity in read
    coverage, after correcting for bias. Here the median $R^2$ across the test
    exons is listed for each method and simple. A positive $R^2$ indicates a
    better fit.\label{tab:pois}}{
    \begin{tabular}{lcccc}\toprule
          & BN    & MART  & GLM   & 7mer \\\midrule
Wetterbom & 0.174 & 0.016 & 0.066 & -0.079 \\
Katze     & 0.280 & 0.243 & 0.158 & 0.033 \\
Bullard   & 0.267 & 0.163 & 0.224 & 0.157 \\
Mortazavi & 0.240 & 0.210 & 0.197 & 0.091 \\
Trapnell  & 0.289 & 0.289 & 0.248 & 0.138
    \end{tabular}
}{}
\end{table}

@@

RNA-Seq is most often used to compare levels of expression, and so a natural
concern is the consistency of the bias between samples. In the data we examined,
the bias appears to be largely, but not entirely consistent (see,
Supplementary Section 5).
%% TODO: which actual section ?
Similarly, in Figure \ref{fig:freqs}, the three data sets
sequenced on the Illumina platform display similar patterns of nonuniformity,
yet differ in magnitude. Batch effects in RNA-Seq remain a legitimate concern,
that should be evaluated and corrected for.
%% TODO: better end sentence
